---
title: "traveltimeR - API Wraper for the Traveltime API"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: true 
    number_sections: true 
    df_print: paged
---

Gets isochrones for traveltimemaps from Traveltime API directly into R. The isochrones display how far you can travel from a certain location within a given timeframe. Supports several modes of transport. 

__GET an API-KEY__ here: http://docs.traveltimeplatform.com/overview/getting-keys/

https://api.traveltimeapp.com/

```{r, message=F, warning=F}
devtools::install_github("tlorusso/traveltimeR")

# load packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, purrr, sf, mapview, traveltimeR)

```

You can easily retrieve the isochrones with the get_traveltime function. Find a list of supported countries here: http://docs.traveltimeplatform.com/overview/supported-countries/

```{r, echo=TRUE, eval=FALSE}
# retrieve data via request 

# The following transport modes are supported:

# "cycling"", "cycling_ferry", "driving", "driving+train", "driving_ferry", "public_transport", 
# "walking", "walking+coach", "walking_bus", "walking_ferry" or "walking_train".

traveltime30 <- get_traveltime(appId="XXXXXXX",
               apiKey="XXXXXXXX",
               location=c(47.378610,8.54000),
               traveltime=1800,
               type="public_transport",
               departure="2018-10-05T08:00:00Z")
```

```{r, echo=FALSE, eval=TRUE}
traveltime30 <- readRDS("traveltime30.RDS")
```

How far you can go from Zurich Mainstation by public transport within 30min visualized with the mapview-package.
```{r}
mapview(traveltime30)
```

